Object-Oriented Internet\\ Cloud Interoperability

### 2021-04-01 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Review ICCS 2021 notification for paper 136 #60
- reviewed the text - for me it works and is ready to be published

\institute
{ Institute of Information Technology, Lodz University of Technology, Łódź, Poland \\
      \email{mailto:mariusz.postol@p.lodz.pl} %\\ \url{http://www.it.p.lodz.pl}
}

@@

Today both obstacles can be overcome, and as examples, we have bank account remote control and voice over IP in daily use. The first application must be fine-tuned in the context of data security, and the second is very sensitive concerning time constraints. Similar approaches could be applied to adopt the concepts well known in process control industry, namely Human Machine Interface (HMI), Supervisory Control and Data Acquisition (SCADA), and Distributed Control Systems (DCS). It is worth stressing that, by design, all of them are designed based on interactive communication. Interactive communication is based on a data polling foundation. If that is the case, the application must follow the interactive behavioral model, because it actively polls the data source for more information by pulling data from a sequence that represents the process state in time. The application is active in the data retrieval process - it controls the pace of the retrieval by sending the requests at its convenience. After dynamically attaching a new island of automation the control application (responsible for the data pulling) must be reconfigured for this interoperability scenario. In other words the interactive communication relationship cannot be directly applied because the control application must be informed on how to pull data from a new source. As a result, a plug and produce scenario \cite{PlugProduceByModellingSkills} cannot be seamlessly applied. A similar drawback must be overcome if for security reasons suitable protection methods have been applied to make network traffic propagation asymmetric. It is accomplished using intermediary devices, for example, firewalls, to enforce traffic selective availability based on predetermined security rules against unauthorized access.

@@

If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied \cite{mpostol2020}. In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the abstract reactive interoperability paradigm. The sessionless relationship is a message distribution scenario where senders of messages, called publishers, do not send them directly to specific receivers, called subscribers, but instead, categorize the published messages into topics without knowledge about which subscribers, if any, there may be. Similarly, subscribers express interest in one or more topics and only receive messages that are of interest, without knowledge about which publishers, if any, there are. In this scenario, the publishers and subscribers are loosely coupled, i.e. they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.

If the \textbf{machine-centric} interoperability - making up islands of automation - must be monitored and/or controlled by a supervisory system, the cloud computing concept may be recognized as a beneficial solution to replace or expand the above mentioned applications, i.e.~HMI, SCADA, DCS, etc. Cloud computing is a method to provide the requested functionality as a set of services. There are many examples that cloud computing is useful to reduce costs and increase robustness. It is also valuable in case the process data must be exposed to many stakeholders. Following this idea and offering control systems as a service, there is required a mechanism created on the service concept and supporting abstraction and virtualization - two main pillars of the cloud computing paradigm. In the cloud computing concept, virtualization is recognized as the possibility of sharing the services by many users, and abstraction hides implementation details.

This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of the Industry 4.0 (I4.0) and Industrial Internet of Things (IIoT) disciplines. For this integration, a new architecture is proposed to support the reactive relationship of communicating parties. To support the multi-vendor environment the OPC Unified Architecture \cite{RefWorks:doc:5ac86c99e4b009947bbb87c6, LiteratureSurveyOnOpenPlatformCommunications, RefWorks:doc:5ac86c99e4b009947bbb87d2} interoperability standard has been selected. Prototyping addresses Microsoft Azure Cloud \cite{MicrosoftAzureIoTPlatform} as an example. The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as an open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet (OOI) \cite{mariusz_postol_2020_4361640, RefWorks:doc:5c6912c9e4b0a562a3fc7f5b, RefWorks:doc:5c66740ae4b081adf5804596}.

@@

\begin{itemize}
      \item reactive M2M interoperability based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype,
      \item cloud interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation,
      \item the proposed generic architecture allows that the gateway functionality is implemented as a composable part at run-time part - no programming required.
\end{itemize}

@@

The described results prove that the \emph{Embedded Gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop the M2M communication compliant with the OPC UA PubSub standard. It is worth stressing that there is no dependency on the Client/Server session-oriented relationship. This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} \cite{RefWorks:doc:5ac86c97e4b009947bbb8728} embedded component of the OPC UA Server. The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to inject the \emph{Embedded Gateway} part into the OPC UA Client/Server to get connected with the cloud in case of the interactive relationship.

In the proposed approach the cloud interoperability is obtained by implementing a dedicated part employing out-of-band communication only without dependency on the OPC UA functionality at all. It is worth stressing that the gateway functionality is implemented as a part - composable to the whole without programming skills. Because the part is composed at the runtime it makes it possible to modify its functionality later after releasing the library or even deploying the application program in the production environment.

>>>>

@@

Today both obstacles can be overcome, and as examples, we have bank account remote control and voice over IP in daily use. The first application must be fine-tuned in the context of data security, and the second is very sensitive concerning time constraints. Similar approaches could be applied to adopt the concepts well known in process control industry, namely Human Machine Interface (HMI), Supervisory Control and Data Acquisition (SCADA), and Distributed Control Systems (DCS). It is worth stressing that, by design, all of them are designed based on interactive communication. Interactive communication is based on a data polling relationship. If that is the case, the application must follow the interactive behavioral model, because it actively polls the data source for more information by pulling data from a sequence that represents the process state in time. The application is active in the data retrieval process - it controls the pace of the retrieval by sending the requests at its convenience. After dynamically attaching a new island of automation the control application (responsible for the data pulling) must be reconfigured for this interoperability scenario. In other words the interactive communication relationship cannot be directly applied because the control application must be informed on how to pull data from a new source. As a result, a plug and produce scenario \cite{PlugProduceByModellingSkills} cannot be seamlessly applied. A similar drawback must be overcome if for security reasons suitable protection methods have been applied to make network traffic propagation asymmetric. It is accomplished using intermediary devices, for example, firewalls, to enforce traffic selective availability based on predetermined security rules against unauthorized access.

@@

If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied \cite{mpostol2020}. In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the reactive interoperability paradigm. The sessionless relationship is a message distribution scenario where senders of messages, called publishers, do not send them directly to specific receivers, called subscribers, but instead, categorize the published messages into topics without knowledge about which subscribers, if any, there may be. Similarly, subscribers express interest in one or more topics and only receive messages that are of interest, without knowledge about which publishers, if any, there are. In this scenario, the publishers and subscribers are loosely coupled, i.e. they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.

If the \textbf{machine-centric} Cyber-Physical System (CPS) - making up islands of automation - must be monitored and/or controlled by a supervisory system, the cloud computing concept may be recognized as a beneficial solution to replace or expand the above mentioned applications, i.e.~HMI, SCADA, DCS, etc. Cloud computing is a method to provide the requested functionality as a set of services. There are many examples that cloud computing is useful to reduce costs and increase robustness. It is also valuable in case the process data must be exposed to many stakeholders. Following this idea and offering control systems as a service, there is required a mechanism created on the service concept and supporting abstraction and virtualization - two main pillars of the cloud computing paradigm. In the cloud computing concept, virtualization is recognized as the possibility of sharing the services by many users, and abstraction hides implementation details.

This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of the Industry 4.0 (I4.0) and Industrial Internet of Things (IIoT) disciplines. For this integration, a new architecture is proposed to support the reactive relationship of communicating parties. To support the multi-vendor environment the OPC Unified Architecture \cite{RefWorks:doc:5ac86c99e4b009947bbb87c6, LiteratureSurveyOnOpenPlatformCommunications, RefWorks:doc:5ac86c99e4b009947bbb87d2} interoperability standard has been selected. The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as an open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}. Prototyping addresses Microsoft Azure Cloud \cite{MicrosoftAzureIoTPlatform} as an example. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet (OOI) \cite{mariusz_postol_2020_4361640, RefWorks:doc:5c6912c9e4b0a562a3fc7f5b, RefWorks:doc:5c66740ae4b081adf5804596}.

@@

\begin{itemize}
      \item reactive M2M interoperability based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype,
      \item cloud interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation,
      \item the proposed generic architecture allows that the gateway functionality is implemented as a composable part at run-time - no programming required.
\end{itemize}

@@

The described results prove that the \emph{Embedded Gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop the M2M communication compliant with the OPC UA PubSub standard. It is worth stressing that there is no dependency on the Client/Server session-oriented relationship. This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} \cite{RefWorks:doc:5ac86c97e4b009947bbb8728} embedded component of the OPC UA Server. The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to inject the \emph{Embedded Gateway} part into the OPC UA Client/Server to get connected with the cloud addressing the interactive relationship.

In the proposed approach the cloud interoperability is obtained by implementing a dedicated part employing out-of-band communication only without dependency on the OPC UA functionality at all. It is worth stressing that the gateway functionality is implemented as a part composable to the whole without programming skills. Because the part is composed at the runtime it makes it possible to modify its functionality later after releasing the library or even deploying the application program in the production environment.
